An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-07-01 conclusion.tex
comments done

\section{Concluding remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by utilization of fixed point iteration. The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
It is possible to combine the approach with an arbitrary master algorithm meaning the approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobian \cite{Palensky2017}. 
The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
We will also look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

>>>>

\section{Concluding remarks}\label{sc:summary}
This work uses a topological ordering of a dependency graph of the interconnected FMUs variable and internal FMU variable connections along with predicates from the FMI specification to calculate a correct initialization order for a co-simulation scenario. 
\claudio{You forgot to mention algebraic loops.}
The plugin optimizes the calculated initialization order by grouping variables with similar characteristics to perform the fewest possible operations in the initialization procedure.
This approach supports the initialization of a co-simulation scenario containing algebraic loops by using fixed point iteration. 
%The approach discards all co-simulation scenarios, not adhering to the law of convergence defined in \cref{def:convergence}.
Our approach is suitable to combine with well-established master algorithms like Gauss-Seidel and Jacobi \cite{Palensky2017}. 
The approach is realized as a plugin for the open-source INTO-CPS Maestro 2 tool and verified against the existing \textit{Initializer} and the calculated initialization order was verified against an established co-simulation Algorithm Generator and Verifier implemented in Prolog\cite{gomes_lucio_vangheluwe_2019}\\
Future work includes formal verification of the plugin using the Logika framework\cite{inbook}.
We will also look into the generation of a verification strategy for the whole Maestro 2 framework to examine how different forms of verification jointly can extend the trust of the correctness of the result of a co-simulation.

### 2020-07-01 relatedwork.tex
comments done

Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS. The publication's purpose is like ours to avoid invalid co-simulation scenarios. Nevertheless, they achieve this by excluding scenarios containing algebraic loops. Their method is like ours realized in a real co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}. Formal methods form the basis of their work, where they have used different kinds of formal methods (Theorem Proving and Model-checking). It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.

>>>>

Amalio et al. \cite{Amalio2016CheckingCo-simulation} has been investigating 
\claudio{Also use present tense here, since it's the paper that we're talking about, and the paper is eternal.}
how to avoid algebraic loops in FMU based co-simulation scenarios by statically checking the architectural design of a CPS. The publication's purpose is like ours to avoid invalid co-simulation scenarios. Nevertheless, they achieve this by excluding scenarios containing algebraic loops. Their method is like ours realized in a real co-simulation tool, INTO-SysML\cite{Miyazawa2016INtegratedModelling}. Formal methods form the basis of their work, where they have used different kinds of formal methods (Theorem Proving and Model-checking). It will be an inspiration for the future work of formally verifying the plugin and other parts of Maestro 2.

\claudio{Also related: \cite{EvoraGomez2019a}. Copy paste from paper content  below (please have a look and rephrase).
A suggestion to distinguish your work from theirs: the resulting algorithm is verified against the simulation semantics (hence the more formal approach.). But this is a weak argument. 
In practice, we will probably need to do more work to really move ahead of the state of the art.
}
{\scriptsize
\begin{verbatim}
The key idea is that a topological sorting of the directed
acyclic graph (DAG) naturally gives the order in which the
variables must be initialised. Therefore, this led to study
how to convert a generic directed graph into a DAG. The
solution found is to build the graph of strongly connected
components (SCC) corresponding to cyclic dependencies.
The resulting graph in which each SCC has been con-
tracted into a single vertex is a DAG. We use Tarjan’s SCC
algorithm (Tarjan, 1972) (used in many Modelica tools) to
identify each SCC in the dependency graph (runs in lin-
ear time). Following the order obtained with a topological
sorting on the contracted SCC graph:
1. for nodes which were not contracted, simply propa-
gate their values
2. for nodes which were contracted (they correspond
to cyclic dependencies), we solve the initialisation
problem using an iterative algorithm called JNRA
(Jacobian based Newton-Raphson Algorithm) in-
spired by traditional Newton-Raphson algorithms of-
ten used for electric load flow computation.
\end{verbatim}
}
